4-examples

### 2022-06-15 4-1-basic.Rmd
section -> Section

A \code{cubble} object can be created from separate spatial and temporal tables in a list, the other arguments (\code{key}, \code{index}, and \code{coords}) are described in section \@ref(create). The function \code{as_cubble()} will automatically try to match the sites in both tables and show a warning message in case of missing information (mismatch between the sites in the two tables).

>>>>

A \code{cubble} object can be created from separate spatial and temporal tables in a list, the other arguments (\code{key}, \code{index}, and \code{coords}) are described in Section \@ref(create). The function \code{as_cubble()} will automatically try to match the sites in both tables and show a warning message in case of missing information (mismatch between the sites in the two tables).
